\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-02-01 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
new recommendations in conclusions

The implication of Theorem~\ref{th:gdistred} is that if the loss function is a monotonic function of $L_{\bm{W}}$ {\color{blue} with some $\bm{W}$ given a priori} then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts.  {\color{blue}  This result does not necessarily involve the covariance of forecast errors unless $\bm{W}$ is explicitly chosen to depend on these covariances.}

@@

The implication of this result is that irrespective of the ${\bm W}$ used in the loss function, an oblique projection based on the forecast error covariance will always minimise {\em expected} loss (where loss is based on squared generalised Euclidean distance).  From the point of view of minimising expected loss, for loss defined in Equation~\ref{eq:GMinTObj}, considerations about sensible weights for an error metric are not relevant.  This will be empirically demonstrated in Section~\ref{sec:EmpStudy}.

@@

}
\section{Bias in forecast reconciliation}\label{sec:BiasInRecon}

@@

\clearpage

{\color{red} I've done a clear page here so we can see the flow better. We will remove this}

\subsection*{Comparison to Base Forecasts}\label{sec:comparebase}

@@

The advantage of MinT however is clearly seen when loss functions are averaged (an estimate of expected loss).  Table~\ref{tab:lossVmethods} reports the relative total error for each loss function. For example, for TSE the relative mean total squared error (RMTSE) is defined as
\begin{equation}
\textrm{RMTSE}^{q}=\frac{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,\label{eq:RTSE}
\end{equation}
where $\textrm{TSE}^{\textrm{Base}}_t$ is the total squared error of the base forecasts at replication $t$.  In contrast with what is displayed in the boxplots, here the average is taken over the replications before taking a ratio.  Table~\ref{tab:lossVmethods} shows that the average loss for MinT is lower than for all other reconciliation methods, irrespective of the loss function used.  This is precisely what would be expected from Theorem~\ref{th:gmint}. For Structural-WSE, a Diebold Mariano test confirms that the average loss for MinT is significantly lower when tested against every other method\footnote{{\color{blue} While differences are not significant for the other loss functions, the scale of the aggregate series leads to a large variance in loss, reducing the power of the test.  Strutural-WSE stablises this effect.}}.

@@

Defining concepts such as coherence and reconciliation in geometric terms provides new insights into hierarchical forecasting methods. We have also provided evidence that bias correction before reconciliation improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation. Our intention in proposing a geometric interpretation is also to provoke research into new areas. We now discuss three such possibilities.

First, it should be possible to extend the concept of coherence {\color{blue}to examples where the coherent space is not a linear plane in $\mathbb{R}^n$.  This includes the case where in addition to aggregation constraints, forecasts are also constrained to be non-negative. We note the work of \cite{wickramasuriya2019optimal} as an attempt to address this issue.  Another possibility is} non-linear constraints where the coherent space may need to be defined by a manifold. Although much more challenging, it is still possible to define reconciled forecasts in terms of projections onto a manifold. Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation, an open question is whether it may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves. Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework. The latter two are issues we investigate in separate papers.

>>>>

The implication of Theorem~\ref{th:gdistred} is that if the loss function is a monotonic function of $L_{\bm{W}}$ {\color{blue} with some $\bm{W}$ given a priori} then the projection matrix $\bm{S}(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$ is guaranteed to improve forecast accuracy over base forecasts.  {\color{blue}  This result does not necessarily involve the covariance of forecast errors unless $\bm{W}$ is explicitly chosen to depend on these covariances.}

@@

The implication of this result is that irrespective of the ${\bm W}$ used in the loss function, an oblique projection based on the forecast error covariance will always minimise {\em expected} loss (where loss is based on squared generalised Euclidean distance).  From the point of view of minimising expected loss, for loss defined in Equation~\ref{eq:GMinTObj}, considerations about sensible weights for an error metric are not relevant.  This is an important caveat to the statement by \cite{VanErven2015a} that \textit{``one should not assume that the choice ${\bm\Sigma}^{-1}=\bm{W}$ will adequately take care of sharing information between hierarchical levels!''}.  While this statement is correct in the context of Theorem~\ref{th:gdistred}, which is the case considered by \cite{VanErven2015a}, it is not true for the objective described in Equation~\ref{eq:GMinTObj}. This will be empirically demonstrated in Section~\ref{sec:EmpStudy}.}

@@

\section{Bias in forecast reconciliation}\label{sec:BiasInRecon}

@@

\subsection{Comparison to Base Forecasts}\label{sec:comparebase}

@@

The advantage of MinT however is clearly seen when loss functions are averaged (an estimate of expected loss).  Table~\ref{tab:lossVmethods} reports the relative total error for each loss function. For example, for TSE the relative mean total squared error (RMTSE) is defined as
\begin{equation}
\textrm{RMTSE}^{q}=\frac{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,\label{eq:RTSE}
\end{equation}
where $\textrm{TSE}^{\textrm{Base}}_t$ is the total squared error of the base forecasts at replication $t$.  In contrast with what is displayed in the boxplots, here the average is taken over the replications before taking a ratio.  Table~\ref{tab:lossVmethods} shows that the average loss for MinT is lower than for all other reconciliation methods, irrespective of the loss function used.  This is precisely what would be expected from Theorem~\ref{th:gmint}. For Structural-WSE, a Diebold Mariano test confirms that the average loss for MinT is significantly lower when tested against every other method\footnote{{\color{blue} While differences are not significant for the other loss functions, the scale of the aggregate series leads to a large variance in loss, reducing the power of the test.  Strutural-WSE stablises this effect.}}.
}

@@

Defining concepts such as coherence and reconciliation in geometric terms provides new insights into hierarchical forecasting methods. {\color{blue} We recommend the following steps for practitioners
\begin{enumerate}
	\item Choose an objective, either
	\begin{enumerate}
		\item To guarantee that reconciled forecasts improve upon base forecasts.
		\item To find the reconciliation method that is best on average.
	\end{enumerate}
    \item Select a ${\bm W}$ to use in loss function $L^2_{\bm W}$ that is well suited to the empirical problem.  For objective (a) our results also apply to any monotonic function of $L^2_{\bm W}$.
    \item Select a reconciliation method.  For objective:
    \begin{enumerate}
    	\item This should be ${\bm G}=({\bm S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$. The dependence in forecast errors is not relevant.
    	\item This should be ${\bm G}=({\bm S}'\bm{\Sigma}^{-1}\bm{S})^{-1}\bm{S}'\bm{\Sigma}^{-1}$. The choice of ${\bm W}$ is not relevant.
    \end{enumerate}
\end{enumerate}}
{\color{blue} Furthermore, for the second objective, base forecasts must be unbiased.  We recommend carrying out} bias correction before reconciliation {\color{blue} and provide evidence that this} improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation.

Our intention in proposing a geometric interpretation is also to provoke research into new areas. We now discuss three such possibilities.  First, it should be possible to extend the concept of coherence {\color{blue}to examples where the coherent space is not a linear plane in $\mathbb{R}^n$.  This includes the case where in addition to aggregation constraints, forecasts are also constrained to be non-negative. We note the work of \cite{wickramasuriya2019optimal} as an attempt to address this issue.  Another possibility is} non-linear constraints where the coherent space may need to be defined by a manifold. Although much more challenging, it is still possible to define reconciled forecasts in terms of projections onto a manifold. Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation, an open question is whether it may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves. Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework. The latter two are issues we investigate in separate papers.
